### 2.3.1 Basic Commands

To create a vector of numbers, we use the function c() for concatenate.

```{r}
x <- c(1,3,2,5)
x
```

We can tell R to add two sets of numbers together given x and y should be the same length.

```{r}
x <- c(1,6,2)
y <- c(1,4,2)
x + y
```

The ls() function allows us to look at a list of all of the objects, such as data and functions, that we have saved so far. The rm() function can be used to delete any that we don't want.

```{r}
ls()
rm(x,y)
ls()
```

The maxtrix() function can be used to create a matrix of numbers.

```{r}
x <- matrix(data=c(1,2,3,4), nrow=2, ncol=2)
x
```

Alternatively, the byrow=TRUE option can be used to populate the matrix in order of the rows.

```{r}
matrix(c(1,2,3,4),2,2,byrow=TRUE)
```

The sqrt() function returns the square root of each element of a vector or matrix.

```{r}
sqrt(x)
```

The command x^2 raises each element of x to the power 2; any powers are possible, including fractional or negative powers.

```{r}
x^2
```

The rnorm() fcuntion generates a vector of random normal variables, with first argument n the sampel size. By default, rnorm() creates standard normal random variables with a mean of 0 and a standard deviation of 1.

```{r}
x <- rnorm(50)
y <- x + rnorm(50, mean=50, sd=.1)
cor(x,y)
```

Sometimes we want our code to reproduce the exact same set of random number; we can use set.seed() function to do this. The set.seed() function takes an (arbitrary) integer argument.

```{r}
set.seed(1303)
rnorm(50)
```

The mean() and var() functions can be used to compute the mean and variance of a vector of numbers. Applying sqrt() to the output fo var() will give the standard deviation. Or we can simply use the sd() function.

```{r}
set.seed(3)
y <- rnorm(100)
mean(y)
var(y)
sqrt(var(y))
sd(y)
```

### 2.3.2 Graphics

The plot() function is the primary way to plot data in R. For instance, plot(x,y) produces a scatterplot of the numbers in x versus the numbers in y.

```{r}
x <- rnorm(100)
y <- rnorm(100)
plot(x,y,xlab="this is the x-axis",ylab="this is the y-axis",main="Plot of X vs Y")
```

We will often want to save the output of an R plot. The command that we use to do this will depend on the file type that we would like to create. For instance, to create a pdf, we use the pdf() function. The function dev.off() indicates to R that we are done creating the plot.

```{r}
pdf("Figure.pdf")
plot(x,y,col="green")
dev.off()
```

The function seq() can be used to create a sequence of numbers. For instance, seq(a,b) makes a vector of integers between a and b.

```{r}
x <- seq(1,10)
x
x <- 1:10
x
x <- seq(-pi,pi,length=10)
x
```

The contour() function produces a contour plot in order to represent three-dimensional data; it is like a topographical map. It takes three arguments:
1. A vector of the x values
2. A vector of the y values
3. A matrix whose elements correspond to the z value (the third dimension) for each pair of (x,y) coordinates

```{r}
y <- x
f <- outer(x,y,function(x,y)cos(y)/(1+x^2))
contour(x,y,f)
contour(x,y,f,nlevels=45,add=T)
fa=(f-t(f))/2
contour(x,y,fa,nlevels=15)
```

The image() function works the same way as contour(). except that it produces a color-coded plot whose colors depend on the z value. This is known as heatmap. Alternatively, persp() can be used to produce a three-dimensional plot.

```{r}
image(x,y,fa)
persp(x,y,fa)
persp(x,y,fa,theta=30)
persp(x,y,fa,theta=30,phi=20)
persp(x,y,fa,theta=30,phi=70)
persp(x,y,fa,theta=30,phi=40)
```

### 2.3.3 Indexing Data




