### 2.3.1 Basic Commands

To create a vector of numbers, we use the function c() for concatenate.

```{r}
x <- c(1,3,2,5)
x
```

We can tell R to add two sets of numbers together given x and y should be the same length.

```{r}
x <- c(1,6,2)
y <- c(1,4,2)
x + y
```

The ls() function allows us to look at a list of all of the objects, such as data and functions, that we have saved so far. The rm() function can be used to delete any that we don't want.

```{r}
ls()
rm(x,y)
ls()
```

The maxtrix() function can be used to create a matrix of numbers.

```{r}
x <- matrix(data=c(1,2,3,4), nrow=2, ncol=2)
x
```

Alternatively, the byrow=TRUE option can be used to populate the matrix in order of the rows.

```{r}
matrix(c(1,2,3,4),2,2,byrow=TRUE)
```

The sqrt() function returns the square root of each element of a vector or matrix.

```{r}
sqrt(x)
```

The command x^2 raises each element of x to the power 2; any powers are possible, including fractional or negative powers.

```{r}
x^2
```

The rnorm() fcuntion generates a vector of random normal variables, with first argument n the sampel size. By default, rnorm() creates standard normal random variables with a mean of 0 and a standard deviation of 1.

```{r}
x <- rnorm(50)
y <- x + rnorm(50, mean=50, sd=.1)
cor(x,y)
```

Sometimes we want our code to reproduce the exact same set of random number; we can use set.seed() function to do this. The set.seed() function takes an (arbitrary) integer argument.

```{r}
set.seed(1303)
rnorm(50)
```

The mean() and var() functions can be used to compute the mean and variance of a vector of numbers. Applying sqrt() to the output fo var() will give the standard deviation. Or we can simply use the sd() function.

```{r}
set.seed(3)
y=rnorm(100)
mean(y)
var(y)
sqrt(var(y))
sd(y)
```

